%!TEX TS-program = lualatex
\documentclass[a4paper, extended]{comcv}

\usepackage[english]{babel}
\usepackage{fontspec}

\title{Vikrom's CV}
\fullname{Vikrom}{Narula}{}
\cvtitle{Software Engineer, Learner, Problem Solver}
\website{https://narula2000.github.io}{narula2000}
\email{vikrom.nar@gmail.com}
\github{https://github.com/narula2000}{GitHub}
\linkedin{https://www.linkedin.com/in/vikrom-narula-36aa33184}{LinkedIn}
\phone{+66869792917}{(+66)869792917}
\currentdate{\today}

\begin{document}
\section{Experiences}
\combosection{\href{https://www.manatal.com/}{Manatal}}{Full-time, Junior Backend Engineer}{Django, Python, FastAPI, PostgreSQL}{Sep 2024-Present}{
  \begin{tightlist}
    \item Owner of multiple micro-service such as, Webhook event distributor, Resume parser.
    \item Lead and implement a logging system for micro-service with Datadog integration.
    \item Lead, design and implement a library to generate notification and transactional emails.
    \item Modernize email to new template via Jinja hydration.
    \item Push and lead the project on standardizing linting for backend micro-service, and set up pre-commit hooks.
    \item Improve local development via dockerization of multiple services, updating \& maintaining a mocking server.
    \item Optimize dashboard page load speed by 40\% via endpoint pruning and optimization.
    \item Optimize slowest endpoint on multiple micro-service.
    \item Create a backfill script for missing key client data from information extracted via history logs.
    \item Generate and maintain weekly engineering reports.
  \end{tightlist}
}

\combosection{\href{https://erd.ai/}{Erudite}}{Full-time, Back-end Engineer}{Next.js, Python, Prisma, Docker, Django, Rust, Go}{Oct 2022-Feb 2024}{
  \begin{tightlist}
    \item Dockerize and deploy candle stick data aggregation service.
    \item Benchmark and write reports on data latency from server to client.
    \item Implement Websocket endpoint for users to subscribe to real-time candlestick data.
    \item Build a candlestick data aggregation service with Rust from raw ITCH data.
    \item Lead micro-service protocol adapter project. Converting ITCH protocol to EMAPI protocol(Completed on time).
    \item Consult and advise on projects architecture and tech stacks.
    \item Attend client meetings to give development perspective.
    \item Lead and documented back-end on medicine registry service. 1st phase was completed in 1 month.
    \item Implement invoice, and receipt service interface to third party clients.
  \end{tightlist}
}

\combosection{\href{https://www.agoda.com/}{Agoda}}{Internship, Finance Back-end Team}{.NET, React, SQL, Play, Scala}{Apr 2022-Aug 2022}{
  \begin{tightlist}
    \item Migrate .NET Framework to .NET Core
    \item Migrate from Github, and Teamcity to Gitlab and it's CI/CD
    \item Implement internal API endpoint to streamline manual workflow, and notify via Slack
    \item Change database usage from Hadoop to Microsoft SQL server for an API endpoint
  \end{tightlist}
}

\combosection{\href{https://thegang.tech/?lang=en}{The Gang Technology}}{Part-time, Back-end Developer}{Django, PostgreSQL}{Jan 2022-Feb 2022}{
  \begin{tightlist}
    \item Implement API endpoint to query user information and parse to xlsx format
    \item Implement API endpoint to query user information and output as pdf format
    \item Implement function to parse user information to government standard encoding
    \item Implement schema to accept government standard encoding
  \end{tightlist}
}

\combosection{\href{https://adhero.co.th}{Ad Hero}}{Full-time, Part-time, Back-end Developer}{React, Prisma, GraphQL, Express.js}{Feb 2020-Dec 2020}{
  \begin{tightlist}
    \item Implement API endpoint to interact with service provider API
    \item Encrypt and decrypt API data for some service provider
  \end{tightlist}
}

\section{Projects}
\combosection{\href{https://github.com/narula2000/wc}{Replicate wc Unix Command}}
{Python, Unix, CLI}{}{}{
  \indent Create a replication of the Unix command wc via Python.
}

\combosection{\href{https://github.com/narula2000/crypto-watcher}{Crypto Currency Analyser}}
{Python, Pandas, BeautifulSoup}{}{}{
  \indent Scrap top market capitalization crypto currency to compare current price
  with average price within some time gap and show percentage change.
}

\vspace{\topsep}
\section{Skills}
\combosection{Programming}{}{}{}{
  \begin{tightlist}
    \item Python (5+ years)
    \item Basic: Rust, SQL, R, HTML, CSS
  \end{tightlist}
}

\combosection{Tools/Others}{}{}{}{
  \begin{tightlist}
    \item Scripting(Bash, Python), Git, Linux/Unix, Docker
    \item Neovim, Visual Studio Code, IntelliJ IDEA, Vim, Tmux, \LaTeX
  \end{tightlist}
}

\section{Education}
\combosection{\href{https://muic.mahidol.ac.th/eng}{Mahidol University International College}}{Bachelor degree in Computer Science}{}{2018-2022}{CGPA 3.10

  \ifextended
    Courses - Advanced Calculus, Statistics, Discrete Math, Algorithm Analysis, Digital Logic Design, Database Management Systems, Data Structures, Operating Systems, Computer Networks, Deep learning, Blockchain
  \else
  \fi
  }

\end{document}
